\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2020-12-29 manuscript.Rnw
Minor updates given new icer() function

\subsubsection{Simulation}
Before constructing each submodel, we specify the number of parameters samples that will be drawn for the PSA.

@@

\subsubsection{Incremental cost-effectiveness ratio}
The \code{cea_pw()} function computes the ICER and a summary table can be produced with \code{icer_tbl()}. The argument \code{k} is the WTP threshold and in this example the new interventions are labeled as``cost-effective'' relative to SOC if the ICER is below this threshold. Incremental QALYs and incremental costs are computed by averaging over PSA samples.

<<cea_icer>>=
icer_tbl(cea_pw_ictstm, colnames = strategies$strategy_name,
         k = 100000)
@

>>>>

\subsubsection{Simulation}
Before constructing each submodel, we specify the number of parameter samples that will be drawn for the PSA.

@@

\subsubsection{Incremental cost-effectiveness ratio}
The \code{cea_pw()} function computes the ICER. A summary table can be produced with \code{icer()} and \code{format()} can format the table for pretty printing. The argument \code{k} is the WTP threshold and is used to compute the INMB. Estimates of incremental QALYs and incremental costs are computed by averaging over PSA samples. By default, 95\% confidence intervals are presented and are computed using quantiles from the PSA.

<<cea_icer>>=
library("magrittr")
icer(cea_pw_ictstm, k = 100000, 
     strategy_values = strategies$strategy_name[-1]) %>%
  format()
@
